\documentclass{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{float}
\usepackage{graphicx}
\usepackage{braket}
\usepackage{hyperref}
\usepackage{color}
\usepackage[]{siunitx}
\usepackage[style=phys,
			articletitle=false,
			biblabel=brackets,
			chaptertitle=false,
			pageranges=false]{biblatex}

% Additional options
\addbibresource{bibliography.bib}
\DeclareSIUnit\Torr{Torr}

% Macros
\newcommand{\tsup}{\textsuperscript}													% superscript outside math mode.
\newcommand{\tsub}{\textsubscript}														% subscript outside math mode.
\newcommand{\Sr}[1]{\tsup{#1}\textnormal{Sr}}											% {}^{xx}Sr outside math mode.
\newcommand{\Srion}[1]{\textnormal{Sr}\tsup{#1}}										% {}Sr^{xx} outside math mode.
\newcommand{\Li}[1]{\tsup{#1}\textnormal{Li}}											% {}^{xx}Li outside math mode.
\newcommand{\SLJ}[3]{\tsup{#1}\textnormal{#2}\tsub{#3}}
\newcommand{\SLJF}[4]{\tsup{#1}\textnormal{#2}\tsub{#3}\textnormal{, }{F = {#4}}}
\newcommand{\nSLJ}[4]{{#1}\textnormal{ }\SLJ{#2}{#3}{#4}}
\newcommand{\nSLJm}[5]{{#1}\textnormal{ }\SLJ{#2}{#3}{#4}\textnormal{, }{m_J = {#5}}}
\newcommand{\nSLJF}[5]{{#1}\textnormal{ }\SLJ{#2}{#3}{#4}\textnormal{, }{F = {#5}}}

% Front matter
\title{Notes on the strontium rydberg data}
\author{Roger Ding}
%\date
 
% Start of the document.
\begin{document}

\maketitle


Some notes on the transcribed data.

\section{Checked/unchecked data tables}

Need to figure out a way to record which tables I have checked and not checked. For now, I can use the commits where I state which tables have been checked.

\section{\fullcite{sul_1938}}

The magical ability of Francine Arizmendez (fariz) at Fondren's ILLiad was able to obtain a copy of this elusive reference. The reference ``F. J. Sullivan, Univ. Pittsburgh Bull. 35, 1 1938'' references the University of Pittsburgh's graduate school bulletin which contains ``abstracts of theses, researches in progress, and bibliography of publications''. In this instance, the bulletin gives Sullivan's observed strontium lines and is likely only part of what's included in Sullivan's Ph.D. thesis. 

To really make sense of the tables, I think I'll need to reference NIST's ASD (for Sr I). In the table, Ref L7362 refers to F. J. Sullivan's UPitt Bulletin. 

\section{\fullcite{esh_1977}}

\subsection{Changes to source material}

\subsubsection{Observed energy of $\nSLJ{5s6d}{3}{D}{2}$}

The calculated energy of the $\nSLJ{5s6d}{3}{D}{2}$ given in Table~IV (the ${J=2}$ states) as \SI{36691.11}{\per\cm} is likely a typo. I think it should be \SI{39691.11}{\per\cm} instead which is supported by \cite{san_2010} where the energy listed for this state is \SI{39690.802}{\per\cm} (i.e., a check that the observed energy is correct). Making this change means the error between observed and calculated energies is now \num{-0.260} and agrees with the error in Table~IV.

\subsubsection{Assignments for ${n=15,16}$ ${\SLJ{1}{D}{2}}$ and ${\SLJ{3}{D}{2}}$ lines}

\citeauthor{esh_1977} doesn't definitively assign ${n=15,16}$ ${\nSLJ{5snd}{1}{D}{2}}$ and ${\nSLJ{5snd}{3}{D}{2}}$ states, instead labeling those four lines as ${\SLJ{1,3}{D}{2}}$.

From \cite{san_2010}, the energy of the ${\nSLJ{5s15d}{3}{D}{2}}$ (${\nSLJ{5s15d}{1}{D}{2}}$) is given as \SI{45276.65}{\per\cm} (\SI{45263.6196}{\per\cm}). Noting that the $\SLJ{1}{D}{2}$ is lower in energy than the $\SLJ{3}{D}{2}$ state, I label the lower (higher) energy state as $\SLJ{1}{D}{2}$ ($\SLJ{3}{D}{2}$).

Similarly for the $5s16d$ states, \cite{san_2010} gives the energy of the $\nSLJ{5s16d}{1}{D}{2}$ ($\nSLJ{5s16d}{3}{D}{2}$) to be \SI{45362.1272}{\per\cm} (\SI{45350.35}{\per\cm}). In this case, the $\SLJ{1}{D}{2}$ is now higher in energy than the $\SLJ{3}{D}{2}$ state so I label them accordingly in my table.

\section{\fullcite{ewp_1976}}

The authors state that they estimate their final uncertainties to be \SI{\pm 0.3}{\per\cm}. 

In Table~1, the authors do not appear to assign $n$-values for $\nSLJ{5snd}{3}{D}{2}$ lines, leaving that part of the table blank. In my data table, I left unassigned or unidentified lines out.

\section{\fullcite{gac_1968}}

In this particular paper, they do not give an uncertainty but in an earlier paper (\cite{gaw_1966}), Garton states their error to be not greater than \SI{0.008}{\angstrom} so I took that to be the uncertainty for their values in the present paper. This also suggests that their measured units are wavelength and not wavenumbers.

I'll need to look into why Table~1 ($\nSLJ{5snp}{1}{P}{1}$) has wavelengths to three decimal places whereas Table~2 ($\nSLJ{5snp}{3}{P}{1}$) only gives wavelengths to two decimals. 

\section{\fullcite{rub_1978}}

This paper measures state energies NOT relative to the ground state. 

They measured wavelengths as their units and gaven an uncertainty of \SI{0.002}{\nm}. 

When I write the analysis code for analyzing the data, I think I'll use the most recent (and hopefully more accurate) measurements of the initial states they're exciting from and then using the measured wavelength and uncertainty to calculate the term energies. Actually, I'll need to figure out how they converted from the wavelength in air to vacuum wavenumber (i.e., what formula they used to account for humidity, temperature, etc.). 

\subsubsection{Notes}

The ``Previous'' column gives the last few digits from the cited source for comparison with this paper's values. 

\section{\fullcite{awe_1979}}

Doesn't seem like there's much to say, they give the energies and uncertainties in wavenumbers. 

\section{\fullcite{blt_1982}}

They don't explicitly specify which isotope they measure the term energies for but it appears to be for \Sr{88}. They used two-photon spectroscopy (retro-reflected blue laser) on strontium heated to \SI{650}{\celsius} (corresponding to \SI{25}{\milli\Torr}). 

\subsubsection{Notes}

They state they are able to measure the Rydberg energies with an accuracy of \num{2E-8}. For now, I calculated the uncertainty assuming they mean an error \num{2E-8} of their measured energies (i.e., multiplying their reported energies by \num{2E-8}) which I'll need to include in the analysis code. 

\section{\fullcite{bls_1982}}

In the ``Experimental'' section, they give an accuracy of \SI{\pm0.15}{\per\cm} for the Sr lines. 

\subsection{Changes to source material}

\subsubsection{Table~4}

There appear to be several errors in Table~4 in particular for ${n=16, 17, 21, 22, 44}$ where ${E_{exp} - E_{Langer}}$ calculated from the table values do not match with ${\Delta E}$ in the table. Using the $\SLJ{3}{S}{1}$ quantum defects from \cite{vjp_2012} (${R_{Sr} = \SI{109736.627}{\per\cm}}$) and the ionization energy from \cite{san_2010} (\SI{45932.1982}{\per\cm} for \Sr{88}), I calculated the expected term energies to see whether $E_{exp}$ or $E_{Langer}$ were incorrect. 

For ${n=16}$: I calculate ${E(n=16) = \SI{45243.85936}{\per\cm}}$ so I think ${E_{Langer}(n=16)}$ is a typo.

For ${n=17}$: I calculate ${E(n=17) = \SI{45341.21285}{\per\cm}}$ so I think ${E_{Langer}(n=17)}$ is a typo. Since the table gives ${\Delta E = 0}$, I set ${E_{Langer} = \SI{45341.28}{\per\cm}}$ (i.e., the $E_{Exp}$ value in the table).

For ${n=21}$: I calculate ${E(n=21) = \SI{45579.039}{\per\cm}}$ so I think ${E_{Langer}(n=21)}$ is a typo. Changing $E_{Langer}$ in the table to \SI{45579.06}{\per\cm} makes ${\Delta E}$ correct.

For ${n=22}$: I calculate ${E(n=22) = \SI{45615.944}{\per\cm}}$ so I think ${E_{Langer}(n=22)}$ is a typo. Changing $E_{Langer}$ in the table to \SI{45615.96}{\per\cm} makes ${\Delta E}$ correct.

For ${n=44}$: I calculate ${E(n=44) = \SI{45865.719}{\per\cm}}$ so I think ${E_{Langer}(n=44)}$ is a typo. Changing $E_{Langer}$ in the table to \SI{45865.72}{\per\cm} makes ${\Delta E}$ correct.

For now, I left the $E_{Langer}$ values in the table since I'm primarily interested in $E_{exp}$.

\section{\fullcite{khk_1993}}

They report energies with uncertainties - not much extra to say.

\section{\fullcite{daz_1995}}

\subsection{To do}

Need to figure out what the superscripts in Table~1 mean...

In the main text, they state that the ``${n < 10}$ states are taken from Ref.~10'' which is \cite{moo_1952v2} and corresponds to superscript b in Table~1. Still no idea what a and c correspond to.

\subsection{Notes}

\subsubsection{Uncertainties}

They don't seem to specify their uncertainties but their PRA paper \cite{daz_1995} (same month and year) suggests an uncertainty of \SI{0.2}{\per\cm} for their measurements of $\nSLJ{5snd}{1,3}{D}{2}$ states. 

\section{\fullcite{dai_1995}}

\subsection{Notes}

The table captions give details about which states are from previous works and which states \citeauthor{dai_1995} measured. The caption also states the uncertainties to be \SI{0.2}{\per\cm} for their measured lines.

\printbibliography

\end{document}